The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2017-12-22 paper/ms.tex
Updated paper

The goal of this catalog is to provide a way to connect a variety of simulations of galaxy cluster mergers within a common interface with multiwavelength observations of real merging clusters, providing an opportunity for observers to compare clusters in their observations with a particular merging scenario. For example, the catalog may be used to interpret existing observations across multiple wavebands such as the Planck-Chandra Cluster Sample\footnote{\url{https://hea-www.harvard.edu/CHANDRA_PLANCK_CLUSTERS/}} \citep{jon16}, or be analyzed to make predictions for what various investigations of real clusters may reveal for future observations and missions, such as {\it Athena}\footnote{\url{http://www.the-athena-x-ray-observatory.eu/}} and {\it Lynx}\footnote{\url{https://wwwastro.msfc.nasa.gov/lynx/}}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{set_page.eps}
\caption{An example ``set page.'' Links are provided to original journal articles, various simulation parameters and other information are tabulated, and links to the data for the individual simulations appear here. This particular page is linked at \url{http://gcmc.hub.yt/virgo/index.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{sim_page.eps}
\caption{An example ``simulation page.'' Slider bars allow exploration of different epochs, and buttons near the top choose different projection axes. The figures link to the page for the files for the corresponding epoch of the simulation. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/index.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{epoch_page.eps}
\caption{An example ``epoch page.'' Links are provided to similar simulations with different physics at the same epoch at the top of the page. For each data type, figures of some of the fields are shown and links to download the data or display in JS9 are provided. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/0046.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{epoch_page2.eps}
\caption{The bottom of an ``epoch page,'' showing the simulated X-ray event file, the link to the Jupyter notebook directions, and the JS9 interface with a projection file loaded, and a circular region selected. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/0046.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{halos_page.eps}
\caption{Another example of a ``simulation page,'' except showing halos from a cosmological simulation instead of epochs. Slider bars allow exploration of different halos, and buttons near the top choose different projection axes. The figures link to the page for the files for the corresponding halo ID. This particular page is linked at \url{http://gcmc.hub.yt/omega500/non_radiative_1.0005/index.html}.}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.95\textwidth]{halo_page.eps}
\caption{A portion of a ``halo page,'' showing the details of the halo information and the slice data for this particular halo. This particular page is linked at \url{http://gcmc.hub.yt/omega500/non_radiative_1.0005/00086.html}.}
\end{center}
\end{figure*}

A number of the simulations have been run using an N-body code to represent the collisionless dark matter component of the cluster via massive particles. A number of these dark matter particles can be sampled from the simulation to represent mock ``galaxies,'' which can also be treated as a collisionless component. For some of these simulations, we have created mock galaxy catalogs.

@@

A ds9 region file containing point regions corresponding to the galaxy positions is provided for each epoch and line-of-sight in addition to the FITS file, which allows the galaxy positions to be plotted over the projections of the other fields.

@@

All of the set pages are linked from the main simulation page, which can be found at \url{http://gcmc.hub.yt/simulations.html}.

@@

Every simulation of a set has a ``simulation page'' which shows various quantities projected perpendicular to the merger plane for every epoch or halo of the simulation that is available. The different epochs or halos can be navigated using a slider bar, and buttons above the slider bar can be used to look at the same images from a different line of sight. The links attached to the images lead to the epoch or halo pages for this simulation.

@@

Any given link on the simulation page leads to an ``epoch page'' or ``halo page'' where images from a particular simulation epoch for idealized simulations, or a particular halo for cosmological simulations, can be examined and the corresponding data may be obtained. Links are provided to similar simulations with different input physics at the same epoch or for the same halo. This page also contains information about the different types of data within the files. A drop-down menu is provided for switching between the different projection axes available.

@@

@@

@@

\bibitem[Jones et al.(2016)]{jon16} Jones, C., Santos, F.~A., Forman, W.~R., et al.\ 2016, American Astronomical Society Meeting Abstracts, 228, 110.04 

@@

>>>>

The goal of this catalog is to provide a way to connect a variety of simulations of galaxy cluster mergers within a common interface with multiwavelength observations of real merging clusters, providing an opportunity for observers to compare clusters in their observations with a particular merging scenario. For example, the catalog may be used to interpret existing observations across multiple wavebands such as the Planck-Chandra Cluster Sample\footnote{\url{https://hea-www.harvard.edu/CHANDRA_PLANCK_CLUSTERS/}} \citep{and17}, or be analyzed to make predictions for what various investigations of real clusters may reveal for future observations and missions, such as {\it Athena}\footnote{\url{http://www.the-athena-x-ray-observatory.eu/}} and {\it Lynx}\footnote{\url{https://wwwastro.msfc.nasa.gov/lynx/}}.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{set_page.eps}
\caption{An example ``set page.'' Links are provided to original journal articles, various simulation parameters and other information are tabulated, and links to the data for the individual simulations appear here. This particular page is linked at \url{http://gcmc.hub.yt/virgo/index.html}.\label{fig:set_page}}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{sim_page.eps}
\caption{An example ``simulation page.'' Slider bars allow exploration of different epochs, and buttons near the top choose different projection axes. The figures link to the page for the files for the corresponding epoch of the simulation. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/index.html}.\label{fig:sim_page}}
\end{center}
\end{figure*}

\begin{figure*}
  \begin{center}
  \includegraphics[width=0.9\textwidth]{halos_page.eps}
  \caption{Another example of a ``simulation page,'' except showing halos from a cosmological simulation instead of epochs. Slider bars allow exploration of different halos, and buttons near the top choose different projection axes. The figures link to the page for the files for the corresponding halo ID. This particular page is linked at \url{http://gcmc.hub.yt/omega500/non_radiative_1.0005/index.html}.\label{fig:halos_page}}
  \end{center}
  \end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{epoch_page.eps}
\caption{An example ``epoch page.'' Links are provided to similar simulations with different physics at the same epoch at the top of the page. For each data type, figures of some of the fields are shown and links to download the data or display in JS9 are provided. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/0046.html}.\label{fig:epoch_page}}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{epoch_page2.eps}
\caption{The bottom of an ``epoch page,'' showing the simulated X-ray event file, the link to the Jupyter notebook directions, and the JS9 interface with a projection file loaded, and a circular region selected. This particular page is linked at \url{http://gcmc.hub.yt/virgo/novisc/0046.html}.\label{fig:epoch_page2}}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.95\textwidth]{halo_page.eps}
\caption{A portion of a ``halo page,'' showing the details of the halo information and the slice data for this particular halo. This particular page is linked at \url{http://gcmc.hub.yt/omega500/non_radiative_1.0005/00086.html}.\label{fig:halo_page}}
\end{center}
\end{figure*}

A number of the simulations have been run using an N-body code to represent the collisionless dark matter component of the cluster via massive particles. A number of these dark matter particles can be sampled from the simulation to represent mock ``galaxies,'' which can also be treated as a collisionless component. For some of these simulations, we have created mock galaxy catalogs, which consist of the sky positions and redshifts of ``galaxy'' particles.

@@

A ds9 region file containing point regions corresponding to the galaxy positions is provided for each epoch and line-of-sight in addition to the FITS file, which allows the galaxy positions to be plotted over the projections of the other fields. At the time of writing, mock galaxy catalogs have been created for the ``A Parameter Space Exploration of Galaxy Cluster Merger'' simulations found at \url{http://gcmc.hub.yt/fiducial/index.html}, an example of which may be found at \url{http://gcmc.hub.yt/fiducial/1to1_b0.5/0139.html}, under the heading ``Galaxies''.

@@

All of the set pages are linked from the main simulation page, which can be found at \url{http://gcmc.hub.yt/simulations.html}. Figure \ref{fig:set_page} shows an example of a set page.

@@

Every simulation of a set has a ``simulation page'' which shows various quantities projected perpendicular to the merger plane for every epoch or halo of the simulation that is available. The different epochs or halos can be navigated using a slider bar, and buttons above the slider bar can be used to look at the same images from a different line of sight. The links attached to the images lead to the epoch or halo pages for this simulation. Simulation pages for a binary merger simulation with different epochs and a cosmological simulation with different halos are shown in Figures \ref{fig:sim_page} and \ref{fig:halos_page}.

@@

Any given link on the simulation page leads to an ``epoch page'' or ``halo page'' where images from a particular simulation epoch for idealized simulations, or a particular halo for cosmological simulations, can be examined and the corresponding data may be obtained. Links are provided to similar simulations with different input physics at the same epoch or for the same halo. This page also contains information about the different types of data within the files. A drop-down menu is provided for switching between the different projection axes available. Examples of epoch and halo pages are shown in Figures \ref{fig:epoch_page}-\ref{fig:halo_page}.

@@

Recently, a similar online catalog of simulated cluster observations been released by \citet{rag16}, which includes 2D maps of relevant quantities, mock X-ray observations, and capabilities for interactive analysis.

@@

\bibitem[Andrade-Santos et al.(2017)]{and17} Andrade-Santos, F., Jones, C., Forman, W.~R., et al.\ 2017, \apj, 843, 76 

@@

@@

\bibitem[Ragagnin et al.(2016)]{rag16} Ragagnin, A., Dolag, K., Biffi, V., et al.\ 2016, arXiv:1612.06380 
